---
title             : "Conducting developmental research online vs. in-person: A meta-analysis"
shorttitle        : "Conducting developmental research online"

author: 
  - name          : "Aaron Chuey"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    email         : "chuey@stanford.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization, Methodology, Formal analysis, Data Curation, Visualization, Writing - Original Draft"
  - name          : "Veronica Boyce"
    affiliation   : "1"
    email         : "vboyce@stanford.edu"
    role:
      - "Conceptualization, Methodology, Formal analysis, Data Curation, Visualization, Writing - Review & Editing"
  - name          : "Anjie Cao"
    affiliation   : "1"
    email         : "anjiecao@stanford.edu"
    role:
      - "Conceptualization, Methodology, Formal analysis, Data Curation, Visualization, Writing - Review & Editing"
  - name          : "Michael C. Frank"
    affiliation   : "1"
    email         : "mcfrank@stanford.edu"
    role:
      - "Conceptualization, Methodology, Formal analysis, Data Curation, Visualization, Writing - Review & Editing, Supervision"

affiliation:
  - id            : "1"
    institution   : "Stanford University, Department of Psychology"

abstract: |
  An increasing number of psychological experiments with children are being conducted using online platforms, in part due to the COVID-19 pandemic. Individual replications have compared the findings of particular experiments online and in-person, but the general effect of online data collection on data collected from children is still unknown. Therefore, the current meta-analysis examines how the effect sizes of developmental studies conducted online compare to the same studies conducted in-person. Our pre-registered analysis includes 211 effect sizes calculated from 30 papers with 3282 children, ranging in age from four months to six years. We examined several moderators of the effect of online testing, including the role of dependent measure (looking vs verbal), online study method (moderated vs unmoderated), and age. The mean effect size of studies conducted in-person was slightly larger than the mean effect size of their counterparts conducted online, a mean difference of d=.12, but this difference was not significant, 95% CI=[.34, -.09]. Additionally, we found no significant moderating effect of dependent measure, online study method, or age. 
  
keywords          : "Methodology, Meta-analysis, Development, Online studies"
wordcount         : "X"
bibliography      : "r-references.bib"
annotate_references: yes

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(googledrive)
library(readxl)
library(metafor)
library(assertthat)
library(glue)
library(wesanderson)
library(gridExtra)
library(here)

library(readxl)

r_refs("r-references.bib")
here::i_am("writing/OnlineMA_main.Rmd")

knitr::opts_knit$set(root.dir = here())
knitr::opts_chunk$set(
                      echo=F, warning=F, 
                      message=F, sanitize = T)

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Public Significance Statement

  For many families, interacting with a researcher online could be their first experience with a scientist, providing developmental science with an unprecedented outreach opportunity. However, to ensure that online research lives up to its potential, it is important to understand whether developmental data obtained online is comparable to data collected in-person. The current meta-analysis finds that studies with children conducted online produce generally similar effect sizes as those conducted in-person, which should empower researchers to make the most of this emerging data collection and outreach opportunity. 

# Introduction 


```{r child = "writing/sections/01_introduction.Rmd"}
```

# Methods 


```{r child = "writing/sections/02_methods.Rmd"}
```

# Results 


```{r child = "writing/sections/03_results.Rmd"}
```

# Discussion


```{r child = "writing/sections/04_discussion.Rmd"}
```


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
