---
title: "Meta-analytic results"
author: "online testing meta-analysis group"
date: "4/7/2022"
output: html_document
---

# Preliminaries and data prep

Meta-analysis inclusion spreadsheet at 

Data file at [https://docs.google.com/spreadsheets/d/1OIrWIsqjuXVBQYdu90AjJ9b--15GfwTjwvqtOhq11oo/edit#gid=0]()

```{r setup}
library(tidyverse)
library(googledrive)
library(readxl)
library(metafor)
library(assertthat)
library(glue)
library(wesanderson)
library(gridExtra)

source("scripts/compute_es.R")
```

Download data.

```{r}
f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1OIrWIsqjuXVBQYdu90AjJ9b--15GfwTjwvqtOhq11oo/edit#gid=0")
googledrive::drive_download(f, overwrite = TRUE)
d <- readxl::read_xlsx("Effect size coding (online testing MA).xlsx")
```

# Data prep and descriptives

```{r}
d <- d |>
  rowwise() |>
  mutate(short_cite = paste(str_c(str_split(authors, pattern = ",")[[1]][1], 
                                  collapse = " "), ":",
                            paste(str_split(main_title, pattern = " ")[[1]][1:2], 
                                  collapse = " ")))
DT::datatable(d)
```
How many effect sizes do we have? 

```{r}
d |>
  ungroup() |>
  summarise(n = n(), 
            n_es = sum(!is.na(d)), 
            n_es_var = sum(!is.na(d_var)))
```

Number of papers and experiments.

```{r}
d |>
  group_by(experiment_ID) |>
  count() %>%
  group_by(n) %>%
  count() %>%
  rename(n_experiments = n, 
         n_papers = nn)
```

Age distribution. 

```{r}
ggplot(d %>% 
         group_by(same_infant) %>% 
         summarise(mean_age_1 = mean(mean_age_1)), 
       aes(x = mean_age_1/12)) + 
  geom_histogram(binwidth = 1) +
  xlab("Mean age (years)") +
  ylab("N groups")
```


Attempt to perform effect size computation. Note that `compute_es.R` is from MetaLab and was used in Bergmann et al. (2018), Child Dev. 

```{r}
d_calc <- d |>
  ungroup() |>
  mutate(idx = 1:n()) |>
  group_by(idx) |>
  nest() |>
  mutate(data = map(data, function (df) {
    es <- compute_es(participant_design = df$participant_design, 
                     x_1 = df$x_1, x_2 = df$x_2, 
                     SD_1 = df$SD_1, SD_2 = df$SD_2, n_1 = df$n_1, n_2 = df$n_2,
                     t = df$t, f = df$F, d = df$d, d_var = df$d_var)
    
    bind_cols(df,es)
  })) |>
  unnest(cols = c(data)) |>
  filter(!is.na(d_calc))
```

Check effect size computation against hand-computed where available. 

```{r}
ggplot(d_calc, 
       aes(x = d, y = d_calc)) + 
  geom_pointrange(aes(ymin = d_calc - d_var_calc, ymax = d_calc + d_var_calc), size=.25) +
  geom_errorbarh(aes(xmin = d - d_var, xmax = d + d_var)) +
  geom_abline(lty =2) + 
  ggrepel::geom_label_repel(aes(label = short_cite))
```
This confirms that -- when we have a hand-computed ES -- it matches the `compute_es.R` ES. 

## create experiment pairs

```{r}
online <- d_calc |> ungroup() |> filter(expt_condition=="online") |>
  mutate(n_2=replace_na(n_2,0), 
         mean_age_2=replace_na(mean_age_2,0),
         online_age=(n_1*mean_age_1+n_2*mean_age_2)/(n_1+n_2),
         online_count=n_1+n_2) |> 
  select(d, d_var, effect_size_group, response_mode, method, short_cite, online_age,online_count) |> 
  rename(d_online=d,d_var_online=d_var)

in_person <-  d_calc |> ungroup()|> filter(expt_condition=="in-person") |> 
   mutate(n_2=replace_na(n_2,0), 
         mean_age_2=replace_na(mean_age_2,0),
         inperson_age=(n_1*mean_age_1+n_2*mean_age_2)/(n_1+n_2),
         inperson_count=n_1+n_2) |> 
  select(d, d_var, effect_size_group, inperson_age, inperson_count) |> 
  rename(d_inperson=d,d_var_inperson=d_var)

pairs <- full_join(online, in_person) |> 
  mutate(d_diff=d_online-d_inperson,
         d_diff_var=d_var_online+d_var_inperson,
         age=(inperson_age*inperson_count+online_age*online_count)/
           (online_count+inperson_count))

paired_mod <- rma.mv(d_diff ~ 1,  
       V = d_diff_var, 
       data = pairs)
```


## Plots with experiment pairs
```{r}
funnel(paired_mod)
```


```{r}

vanilla_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  theme_minimal()

age_plot = ggplot(pairs, aes(x = age, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_smooth(method="lm")+
  geom_pointrange(alpha = .5, position=position_dodge2(width=1)) +
  #coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("Age in Months") +
    #scale_color_continuous(name="Age (Months)") +
  theme_minimal()

looking_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(aes(color=response_mode),alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
scale_color_manual(values = wes_palette("Darjeeling1", n = 2), name = "Measure", labels = c("Looking", "Non-looking")) +
  theme_minimal()
 
moderated_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(aes(color=method),alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
scale_color_manual(values = wes_palette("Cavalcanti1", n = 2), name = "Online method", labels = c("Moderated", "unmoderated")) +
  theme_minimal()
 

vanilla_plot
age_plot
looking_plot
moderated_plot
```


## funnel plot 

```{r}

default_mod <- rma.mv(d_calc ~ 1,  
       V = d_var_calc,
       random = ~1 | as.factor(experiment_ID) / as.factor(same_infant), 
       data = d_calc)


only_online <- rma.mv(d_calc ~ 1,  
       V = d_var_calc,
       random = ~1 | as.factor(experiment_ID) / as.factor(same_infant), 
       data = d_calc %>% filter(expt_condition == "online"))

only_inperson <- rma.mv(d_calc ~ 1,  
       V = d_var_calc,
       random = ~1 | as.factor(experiment_ID) / as.factor(same_infant), 
       data = d_calc %>% filter(expt_condition == "in-person"))
```

```{r}
funnel(default_mod)                   
funnel(only_online)
funnel(only_inperson)
```

```{r}
#all data
regtest(x=d, vi=d_var, data=d_calc)

regtest(x=d, vi=d_var, data=d_calc %>% filter(expt_condition == "online"))

regtest(x=d, vi=d_var, data=d_calc %>% filter(expt_condition == "in-person"))



```




# Main analysis

## Confirmatory meta-analysis

from prereg:

> Following Chuey et al. (2021), we will use a random effects meta-analytic model with a further grouping factor for each experiment pair (lab vs. online) to account for methodological grouping, e.g.:  effect size ~ online_offline + (1 |  experiment).

Note that we group by experimental paradigm (`experiment_ID`) in our preregistration, but this step does not eliminate the dependency between multiple measurements from the same children (e.g., both eye-tracking and video coding of the same data from the same children) if they contribute multiple effect sizes. In order to deal with this, we include a random effect grouping term (`same_infant`). 

```{r}
main_mod <- rma.mv(yi = d_calc, 
                   V = d_var_calc,
                   mods = as.factor(expt_condition),
                   random = ~1 | as.factor(paper_ID)/
                     as.factor(experiment_ID)/
                     as.factor(same_infant)/
                     as.factor(idx), 
                   slab = short_cite, 
                   data = d_calc)
summary(main_mod)
round(main_mod$sigma2, 3)
```

Check unweighted means. This incorrect approach is a good way to spot check if something is badly wrong. Indeed the mean difference is that online study ES are around .19 smaller. But a lot of the smallest ES are grouped within specific studies...

```{r}
d_calc |>
  group_by(expt_condition) |>
  summarise(n = n(), 
            d = mean(d_calc))
```



```{r}
forest(main_mod)
```

Plot of effect size differences (subtracted SMD). 

```{r}
d_diff <- d_calc |>
  group_by(paper_ID, experiment_ID) %>%
  summarise(d_diff = mean(d_calc[expt_condition == "online"], na.rm=TRUE) - 
              mean(d_calc[expt_condition == "in-person"], na.rm=TRUE), 
            age = mean(mean_age_1)) 

# need to be careful with this because this merge can add rows
d_diff <- d_diff |>
  left_join(d_calc |> 
              ungroup() |>
              select(paper_ID, experiment_ID, short_cite) |> 
              distinct())

smd_plot1 = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(alpha = .5, width = .25, height = 0) + 
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  ylab("SMD difference (online - in-person)") + 
  xlab("")
smd_plot1
```


## Confirmatory moderators

>We will consider the following moderators in independent, separate moderated models:
* The type of online method:Moderated / Synchronous method (e.g., using Zoom/Skype with an experimenter) vs.Unmoderated / Asynchronous (e.g. using platform such as LookIt)
* Response Mode: Looking (e.g., looking time, looking location, eye-tracking, lookaways, etc.) vs.Non-looking (e.g. Verbal response, pointing, etc) 
* Mean age of the children participated in the study (months)

### Moderated vs. Unmoderated

The structure of this model is that we create an additional dummy-coded predictor, which is 1 for unmoderated online experiments and 0 otherwise. 

```{r}
moderated_mod <- rma.mv(yi = d_calc, 
                        V = d_var_calc, 
                        mods = ~ as.factor(expt_condition) 
                        + as.factor(method),
                        random = ~1 | as.factor(paper_ID)/
                     as.factor(experiment_ID)/
                     as.factor(same_infant)/
                     as.factor(idx), 
                        slab = short_cite, 
                        data = d_calc)
summary(moderated_mod)
moderated_mod$tau2
```
Sanity check of these estimated with unweighted means. Obviously incorrect, but if this looks different, we should debug. 

```{r}
d_calc |>
  group_by(expt_condition, method) |>
  summarise(d = mean(d_calc), 
            n = n())
```
### Looking time vs. non-looking time

Same approach as above, except that we need an interaction term because some of the in-person effect sizes have a looking time measure as well.

```{r}
looking_mod <- rma.mv(yi = d_calc, 
                      V = d_var_calc, 
                      mods = ~ as.factor(expt_condition) 
                      * as.factor(response_mode),
                      random = ~1 | as.factor(paper_ID)/
                     as.factor(experiment_ID)/
                     as.factor(same_infant)/
                     as.factor(idx), 
                      slab = short_cite, 
                      data = d_calc)
summary(looking_mod)
```
Sanity check of these estimated with unweighted means. Obviously incorrect, but if this looks different, we should debug. 

```{r}
d_calc |>
  group_by(expt_condition, response_mode) |>
  summarise(d = mean(d_calc), 
            n = n())
```

### Age as moderator

To test age, we again look at the interaction, this time of `age` and `expt_condition`. Need to center age. 

```{r}
d_calc$age_centered_mo <- d_calc$mean_age_1 - mean(d_calc$mean_age_1)
age_mod <- rma.mv(yi = d_calc, 
                        V = d_var_calc, 
                        mods = ~ as.factor(expt_condition) 
                        * age_centered_mo,
                        random = ~1 | as.factor(paper_ID)/
                     as.factor(experiment_ID)/
                     as.factor(same_infant)/
                     as.factor(idx), 
                        slab = short_cite, 
                        data = d_calc)
summary(age_mod)
```

CDS Graphs - SMD by online vs in-person + looking/non-looking + moderated/unmoderated
```{r}
d_diff <- d_calc |>
  group_by(paper_ID, experiment_ID) %>%
  summarise(d_diff = mean(d_calc[expt_condition == "online"], na.rm=TRUE) - 
              mean(d_calc[expt_condition == "in-person"], na.rm=TRUE),
            Age = mean(mean_age_1),
            Measure = response_mode[expt_condition == "online"],
            Online_Method = method[expt_condition == "online"]) 
d_diff

# need to be careful with this because this merge can add rows
d_diff <- d_diff |>
  left_join(d_calc |> 
              ungroup() |>
              select(paper_ID, experiment_ID, short_cite) |> 
              distinct())
d_diff
```

```{r}
blank_plot = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(alpha=0) +
  coord_flip() +
  #scale_x_discrete(labels = c("Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite, d_diff, sum)) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  #scale_fill_manual(values = wes_palette("Chevalier1", n = 2), name = "Online method", labels = c("Moderated", "Unmoderated")) +
  theme_minimal()

vanilla_plot = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(alpha = .7, width = .25, height = .25, size = 3) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
 # scale_x_discrete(labels = c("Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  #scale_fill_manual(values = wes_palette("Chevalier1", n = 2), name = "Online method", labels = c("Moderated", "Unmoderated")) +
  theme_minimal()
  #theme(legend.position="none")

om_plot = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(aes(color = Online_Method), alpha = .7, width = .25, height = .25, size = 3) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  scale_color_manual(values = wes_palette("Cavalcanti1", n = 2), name = "Online method", labels = c("Moderated", "unmoderated")) +
  theme_minimal()
  #theme(legend.position="none")

m_plot = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(aes(color = Measure), alpha = .7, width = .25, height = .25, size = 3) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  scale_color_manual(values = wes_palette("Darjeeling1", n = 2), name = "Measure", labels = c("Looking", "Non-looking")) +
  theme_minimal()
  #theme(legend.position="none")

a_plot = ggplot(d_diff, aes(x = short_cite, y = d_diff)) + 
  geom_point(aes(color = Age), alpha = .7, width = .25, height = .25, size = 3) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  scale_color_continuous(name="Age (Months)") +
  theme_minimal()
  #theme(legend.position="none")

blank_plot
vanilla_plot
om_plot
m_plot
a_plot
```


## Exploratory meta-analysis

>We will also code the following fields for exploratory analysis: 
>Attrition rate: the proportion of children participated in the study but not included in the final analysis.
>Number of trials: the number trials included in the experiment. 
>Matching response mode: whether the in-person experiment and the online method has the matching response mode. 

>As an exploratory step we will consider the inclusion of publication-bias diagnostics, but we do not focus on these methods here because 1) our primary hypothesis of interest is not about individual effects but about the contrast between effects, and 2) we are not certain whether the bias would be to publish pairs of effects that are different or similar. 

## equivalence test

```{r}
#load equivalence testing library
library(TOSTER)

#aggregate d's by modality and study
d_online = d_calc %>% 
  filter(expt_condition == "Online") %>%
  group_by(expt_num) %>% 
  summarise(mean_d = mean(d))

d_inperson = d_calc %>% 
  filter(expt_condition == "In-person") %>% 
  group_by(expt_num) %>% 
  summarise(mean_d = mean(d))

#equivalence threshold
threshold = .2

TOSTtwo(m1=mean(d_inperson$mean_d),m2=mean(d_online$mean_d),sd1=sd(d_inperson$mean_d),sd2=sd(d_online$mean_d),n1=nrow(d_inperson),n2=nrow(d_online),low_eqbound_d=-threshold, high_eqbound_d=threshold, alpha = 0.05, var.equal=FALSE)
```
## analysis of n

```{r}
library(lme4)
library(jtools)

d_calc_n = d_calc %>% 
  mutate(experiment_ID = as.factor(experiment_ID)) %>% 
  mutate(same_infant = as.factor(same_infant))
lmer(n_1 ~ expt_condition + (1 | experiment_ID / same_infant), data=d_calc_n) %>% summ()

```