---
title: "SkerrySpelke2014_Replication"
author: "Alexis Smith-Flores"
date: "5/5/2022"
output:
  pdf_document: default
  html_document: default
---
```{r Importing, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(gsheet)
library(ggpubr)
library(rstatix)
library(tayloRswift)
library(scales)
```

# Importing Data and Condition Information
This chunk of code imports the original Skerry & Spelke (2014) data with 10 month olds (line 23) and the conceptual replication data with 11 and 17 month olds (line 24).

```{r, include=FALSE}
#Import Data
skerry.data <- read_csv(here("Data", "skerry.data.csv"))
smithflores.data <- read_csv(here("Data", "smithflores.data.csv"))
```

#Skerry & Spelke (2014)
Reformatting data to match Smith-Flores data.
```{r}
skerry.data = skerry.data%>%
  select(`Subject ID`, Condition, `CompleteFirst?`, EmoOrder, HC:SF)%>%
  rename(sub.num = `Subject ID`,
         experiment = Condition, 
         block.order = `CompleteFirst?`,
         test.order = EmoOrder, 
         complete.happy = HC,
         complete.sad = SC,
         failed.happy = HF,
         failed.sad = SF)%>%
  pivot_longer(cols = complete.happy:failed.sad, 
               names_to = "block.type.trial", 
               values_to = "looking")%>%
  separate(block.type.trial, into = c("block.type", "trial.type"))%>%
  mutate(experiment = ifelse(experiment == "eaeg", "skerry"),
        test.order = ifelse(test.order == "SH", "sad.first", "happy.first"),
        block.order = ifelse(block.order == 1, "complete.first", "failed.first"),
        congruency = ifelse(block.type == "complete" & trial.type == "happy" | 
                              block.type == "failed" & trial.type == "sad", "congruent", "incongruent"))
```

"To confirm that both age groups exhibit sensitivity to emotional congruency, we conducted a separate repeated measures ANOVA for each age group and found main effects of congruency in the 10-month-old group (F(1, 31) = 4.159, p = 0.050)..."

Effect size: generalized eta squared = 0.013
```{r}
skerry.data%>%
  anova_test(dv = looking, 
             wid = sub.num, 
             within = c(congruency, block.type))
```

# Smith-Flores Conceptual Replications
In our first pre-registered experiment we conceptually replicated Skerry & Spelke (2014) using an additional agent. The rest of the stimuli was closely matched. Our preregistration and methods can be found here: `https://osf.io/5cf3x`

Using the same repeated measures ANOVA Skerry & Spelke used, we found a main effect of congruency in the 11 month olds (F(1, 29) = 5.870, p = .022). 

Effect size: generalized eta squared = 0.026
```{r}
smithflores.data = smithflores.data%>%
  mutate(congruency = ifelse(block.type == "complete" & trial.type == "happy" | 
                               block.type == "failed" & trial.type == "sad", 
                             "congruent", 
                             "incongruent"))

smithflores.data%>%
  filter(experiment == "younger")%>%
  anova_test(dv = looking, 
             wid = sub.num, 
             within = c(congruency, block.type))

```

In our second pre-registered experiment we more closely replicated Skerry & Spelke (2014) using an older age group (17-month-olds. Our preregistration and methods can be found here: `https://osf.io/q4t97`

Using the same repeated measures ANOVA Skerry & Spelke used, we found a main effect of congruency in the 11 month olds (F(1, 35) = 5.202, p = .029). 

Effect size: generalized eta squared = 0.015
```{r}

smithflores.data%>%
  filter(experiment == "older")%>%
  anova_test(dv = looking, 
             wid = sub.num, 
             within = c(congruency, block.type))

```
