
```{r result-setup}
library(tidyverse)
library(googledrive)
library(readxl)
library(metafor)
library(assertthat)
library(glue)
library(wesanderson)
library(gridExtra)
library(here)
source(here("scripts/compute_es.R"))
knitr::opts_chunk$set(
                      echo=F, warning=F, 
                      message=F, sanitize = T)

d <- readxl::read_xlsx(here("Effect size coding (online testing MA).xlsx"))

d <- d |>
  rowwise() |>
  mutate(short_cite = paste(str_c(str_split(authors, pattern = ",")[[1]][1], 
                                  collapse = " "), ":",
                            paste(str_split(main_title, pattern = " ")[[1]][1:2], 
                                  collapse = " ")))
d_calc <- d |>
  ungroup() |>
  mutate(idx = 1:n()) |>
  group_by(idx) |>
  nest() |>
  mutate(data = map(data, function (df) {
    es <- compute_es(participant_design = df$participant_design, 
                     x_1 = df$x_1, x_2 = df$x_2, 
                     SD_1 = df$SD_1, SD_2 = df$SD_2, n_1 = df$n_1, n_2 = df$n_2,
                     t = df$t, f = df$F, d = df$d, d_var = df$d_var)
    
    bind_cols(df,es)
  })) |>
  unnest(cols = c(data)) |>
  filter(!is.na(d_calc))
```




```{r forest, fig.env="figure", fig.pos = "h", fig.align = "center",out.width="100%", fig.width=10, fig.height=5, fig.cap = "Forest plots of studies. Each dot is the difference between and in-person measure and a corresponding online measure. In left and center plots, each row is one study (paper or pair of papers). On right plot, y-axis is the average age of the children in the two samples being compared." }

online <- d_calc |> ungroup() |> filter(expt_condition=="online") |>
  mutate(n_2=replace_na(n_2,0), 
         mean_age_2=replace_na(mean_age_2,0),
         online_age=(n_1*mean_age_1+n_2*mean_age_2)/(n_1+n_2),
         online_count=n_1+n_2) |> 
  select(d, d_var, effect_size_group, response_mode, method, short_cite, online_age,online_count) |> 
  rename(d_online=d,d_var_online=d_var)

in_person <-  d_calc |> ungroup()|> filter(expt_condition=="in-person") |> 
   mutate(n_2=replace_na(n_2,0), 
         mean_age_2=replace_na(mean_age_2,0),
         inperson_age=(n_1*mean_age_1+n_2*mean_age_2)/(n_1+n_2),
         inperson_count=n_1+n_2) |> 
  select(d, d_var, effect_size_group, inperson_age, inperson_count) |> 
  rename(d_inperson=d,d_var_inperson=d_var)

pairs <- full_join(online, in_person) |> 
  mutate(d_diff=d_online-d_inperson,
         d_diff_var=d_var_online+d_var_inperson,
         age=(inperson_age*inperson_count+online_age*online_count)/
           (online_count+inperson_count))
vanilla_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
  theme_minimal()

age_plot = ggplot(pairs, aes(x = age, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_smooth(method="lm")+
  geom_pointrange(alpha = .5, position=position_dodge2(width=1)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
 # aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("Age in Months") +
    #scale_color_continuous(name="Age (Months)") +
  theme_minimal()

looking_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(aes(color=response_mode),alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
scale_color_manual(values = wes_palette("Darjeeling1", n = 2), name = "Measure", labels = c("Looking", "Verbal")) +
  theme_minimal()+
    theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "bottom")

 
moderated_plot = ggplot(pairs, aes(x = short_cite, y = d_diff, ymin=d_diff-d_diff_var,
                                 ymax=d_diff+d_diff_var)) + 
  geom_pointrange(aes(color=method),alpha = .5, position=position_dodge2(width=.5)) +
  coord_flip() +
  geom_hline(yintercept = 0, lty = 2) + 
  aes(x=reorder(short_cite,-d_diff, sum)) +
  #scale_x_discrete(labels = c("Paper 24","Paper 23","Paper 22","Paper 21","Paper 20","Paper 19","Paper 18","Paper 17","Paper 16","Paper 15", "Paper 14", "Paper 13", "Paper 12", "Paper 11", "Paper 10", "Paper 9", "Paper 8", "Paper 7", "Paper 6", "Paper 5", "Paper 4", "Paper 3", "Paper 2", "Paper 1")) +
  ylab("SMD difference (online - in-person)") + 
  xlab("") +
scale_color_manual(values = wes_palette("Cavalcanti1", n = 2), name = "Online method", labels = c("Moderated", "Unmoderated")) +
  theme_minimal()+
  theme(axis.text.y=element_blank(), axis.ticks.y=element_blank(), legend.position = "bottom")
 

#vanilla_plot
#age_plot
#looking_plot

library(cowplot)
library(patchwork)
moderated_plot+looking_plot+age_plot
```







```{r coeffs, fig.pos="ht"}
main_mod <- rma.mv(yi = d_calc, 
                   V = d_var_calc,
                   mods = as.factor(expt_condition),
                   random = ~1 | as.factor(experiment_ID) + as.factor(same_infant), 
                   slab = short_cite, 
                   data = d_calc)
#summary(main_mod)

moderated_mod <- rma.mv(yi = d_calc, 
                        V = d_var_calc, 
                        mods = ~ as.factor(expt_condition) 
                        + as.factor(method),
                        random = ~1 | as.factor(experiment_ID) + 
                          as.factor(same_infant), 
                        slab = short_cite, 
                        data = d_calc)
#summary(moderated_mod)

looking_mod <- rma.mv(yi = d_calc, 
                      V = d_var_calc, 
                      mods = ~ as.factor(expt_condition) 
                      * as.factor(response_mode),
                      random = ~1 | as.factor(experiment_ID) + 
                        as.factor(same_infant), 
                      slab = short_cite, 
                      data = d_calc)
#summary(looking_mod)

d_calc$age_centered_mo <- d_calc$mean_age_1 - mean(d_calc$mean_age_1)
age_mod <- rma.mv(yi = d_calc, 
                        V = d_var_calc, 
                        mods = ~ as.factor(expt_condition) 
                        * age_centered_mo,
                        random = ~1 | as.factor(experiment_ID) + 
                          as.factor(same_infant), 
                        slab = short_cite, 
                        data = d_calc)
#summary(age_mod)
library(stringr)
pull_coeffs <- function(mod){
  df <- tibble(Coefficient=rownames(mod$b), Estimate=mod$b |> round(2), `P-value`=mod$pval |> round(3), lower=mod$ci.lb |> round(2), upper=mod$ci.ub |> round(2)) |> 
    mutate(`95% CI`=str_c("[",lower,", ", upper,"]")) |> 
    select(Coefficient, Estimate, `95% CI`, `P-value`) |> 
    mutate(Coefficient=str_replace_all(Coefficient,coll("as.factor(expt_condition)"),"") |> 
             str_replace_all(coll("as.factor(response_mode)"),"") |>
             str_replace_all(coll("as.factor(method)"),"") |>
             str_replace_all(coll("mods"),"online") |> 
             str_replace_all("intrcpt", "Intercept"))
  
  df
}

stats_text  <- function(model, row){
  str_c("Est=", model[row,2], ", 95% CI=", model[row,3],", p=", model[row,4])
}

library(papaja)
library(kableExtra)
pull_coeffs(main_mod) |> 
union(pull_coeffs(looking_mod)) |> 
  union(pull_coeffs(age_mod)) |> 
  union(pull_coeffs(moderated_mod)) |> 
  select(Coefficient, Estimate, `95% CI`, `P-value`) |> 
knitr::kable(caption = "Table of coefficients for the pre-registered models. The overall model is shown first, followed by the three models with moderators.", booktabs=T, format="latex", linesep="") |> 
  pack_rows("Overall", 1, 2) %>%
pack_rows("Looking v Verbal", 3, 6) %>%
pack_rows("Age", 7, 10) |>
  pack_rows("Moderated v Un-moderated", 11, 13) |> 
  kable_styling(latex_options = "hold_position")
  
```

## Confirmatory Analysis

Overall, the meta-analysis estimated a small negative, non-significant effect of online study modality, `r pull_coeffs(main_mod) |> stats_text(2)`. Additionally, we did not find any significant effect of our preregistered moderators or any significant interactions between the moderators and study modality. See Table \@ref(tab:coeffs) for coefficient values. Figure \@ref(fig:forest) shows the effect size differences of experiments by moderators. 


## Exploratory Analysis

```{r funnel, fig.env="figure", fig.pos = "h", fig.align = "center",out.width="80%", fig.width=6, fig.height=4, fig.cap = "Funnel plot of the differences in effect size between pairs of in-person and online studies. A positive observed outcome means the online study had a large effect. \\label{funnel}" }

# library(magick)
paired_mod <- rma.mv(d_diff ~ 1,  
       V = d_diff_var, 
       data = pairs)

funnel(paired_mod)

```
```{r}
funtest <- regtest(x=d_diff, vi=d_diff_var, data=pairs)

```

We conducted an exploratory analysis of potential publication bias. It was unclear how we might expect publication biases to manifest themselves, given that there is some possibility of notoriety for either showing *or* failing to show differences between online and in-person testing.

We analyzed publication bias in the differences in effect sizes between each online and in-lab pair of samples. This analysis checks for publication bias on the basis of whether online studies match the results of the in-person studies. For each online and in-person pair on the same study, we calculated a standard mean difference in effect size between the two studies as well as the variance of this difference. The resulting funnel plot is shown in Figure \@ref(fig:funnel). According to Egger's regression test for funnel plot asymmetry, this plot is asymmetric (p=`r funtest$pval |> round(4)`) and the limit estimate of the effect as standard error goes to zero is `r funtest$est |> round(2)` [`r funtest$ci.lb |> round(2)`, `r funtest$ci.ub |> round(2)`].  Overall, we found no clear bias to publish papers with either larger or smaller differences in effect size than expected. 

<!-- We also considered the overall average age of participants in the pair of studies, as well as the response mode and method of the online sample as moderators. To that end, we found that neither age, dependent measure, nor online study method significantly moderated the difference in effect size between online and in-person studies. -->
